
# Enhancing Lead Monetization

Total revenue by product

```{r}
market_prod_matches %>%
  group_by(CATEGORY_NAME) %>%
  summarise(Revenue = sum(REVENUE)) %>%
  arrange(desc(Revenue))
```

Revenue per lead by product shows which products are monetized the most and least effectively.

```{r}
market_prod_matches %>%
  group_by(CATEGORY_NAME) %>%
  summarise(Revenue_PerLead = sum(REVENUE)/n_distinct(LEAD_ID)) %>% # number of sessions per channel
  arrange(desc(Revenue_PerLead))
```


Now that I have identified which products generate the most revenue, I will explore the make up of products for all referrals.

```{r}
total_refs <- nrow(market_prod_matches)

market_prod_matches %>%
  group_by(CATEGORY_NAME) %>%
  summarise(rows_by_cat = n()) %>%
  mutate(Proportion_of_Total_Refs = rows_by_cat / total_refs)

```

Proportion of products within each marketing channel. Distribution of products within each channel.

```{r}
total_rows_per_channel <- market_prod_matches %>%
  group_by(CHANNEL) %>%
  summarise(Total_Rows = n())

# Calculate the product count for each category within each channel
table <- market_prod_matches %>%
  group_by(CHANNEL, CATEGORY_NAME) %>%
  summarise(Product_Count = n()) %>%
  ungroup() %>%
  left_join(total_rows_per_channel, by = "CHANNEL") %>%
  mutate(Proportion = Product_Count / Total_Rows) %>%
  arrange(CHANNEL, desc(Product_Count))
table

```

Proportion of products stratified by the associated marketing channel. Distribution of product counts within each category.

```{r}
total_rows_per_cat <- market_prod_matches %>%
  group_by(CATEGORY_NAME) %>%
  summarise(Total_Rows = n())

market_prod_matches %>%
  group_by(CATEGORY_NAME, CHANNEL) %>%
  summarise(Product_Count = n()) %>%
  ungroup() %>%
  left_join(total_rows_per_cat, by = "CATEGORY_NAME") %>%
  mutate(Proportion = Product_Count / Total_Rows) %>%
  arrange(CATEGORY_NAME, desc(Product_Count))
```
